---
title: "1_chunks_and_packages"
output: html_document
---

## Guiding principles / recurring themes

**"Keep the raw data raw"** — A hard line separating raw data and analyses. In R, we have data in one file and written computational commands saved as a separate file.

**Think ahead for Future You, Future Us.** Help make lives easier — first and foremost your own. Create breadcrumbs for yourselves and others: document and share your work. 

(https://github.com/rstudio-conf-2020/r-for-excel)[R for Excel user]

This is a called a chunk. We have given it a name called _setup_.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We can press play to execute the code in the chunk.

Pacakges in the context of R are like apps for your phone.
Things that provide specific functionality.
For example, below is a way to install a package for graphics called `ggplot`.

```{r packages}
#install.packages("ggplot")
```

You load a package into your current working enviroment -
Each project has its own environment

```{r loading_package}
#library("ggplot")
```

In our short tutorial, we are going to follow series of packages - called Tidyverse.
You can load all these packages together.

```{r load_tidyverse, warning=FALSE}
library(tidyverse)
```




