---
title: "2_variables_and_data_frames"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For example, here is a simple variable (a way to store the data)

```{r variable, }
workshop_name = "Introduction to R workshop"
workshop_name
```

We also have in-built data sets. These are useful for practice.
```{r}
cars
```

## %>%

This is the weirdest symbol you are going to come across.

It's called a pipe.

It basically says take a thing(data) from left and past it to the right.

For example, if I want to filter the `cars` dataset for `speed==4`

```{r}
cars %>% filter(speed==4)
```
# Congratulations, now you know how to filter a data set!

You can filter on multiple columns.

```{r}
cars %>% filter(speed==4) %>% filter(dist==2)
```


```{r}
cars %>% ggplot(aes(x = speed, y = dist))
```

```{r}
cars %>% ggplot(aes(x = speed, y = dist)) + geom_point(alpha = 0.8, colour = "red", size = 4) 
```

Let's play with a bit bigger data set.

```{r}
library(gapminder)
```

```{r}
gapminder
```

```{r}
gapminder %>% 
  ggplot(aes(x = year, y = lifeExp, group = country)) +
  geom_line(colour = "gray") +
  facet_wrap(~continent) +
  theme_bw()
```

